|

### 2016-05-18 manuscript/manuscript_pve.Rmd
thesis edits, only added to manuscript if appropriate
adds a few new cites

apparently i didnt push the CUE plots for BM yet

\
One approach to examine the coordination of *A*~n~ and growth is to manipulate C source activity. Examples include elevated CO~2~ and partial defoliation experiments. Elevated CO~2~ has been shown to increase *A*~n~ [@drake1997more; @ainsworth2007response]; across four forest Free-Air CO~2~ Enrichment (FACE) experiments this increased photosynthetic uptake resulted in a stimulation of biomass production by 23 % on average [@norby2005forest]. Evidence from a wide range of elevated CO~2~ experiments, however, also reveals that even with an average photosynthetic enhancement of over 30 %, the biomass growth rate only increases by around 10 % [@kirschbaum2011does]. In partial defoliation experiments, increases in *A*~n~ of the remaining foliage are commonly shown, and are attributed to reduction in end-product inhibition [@iglesias2002regulation; @zhou2003changes; @handa2005test], enhanced biochemical activity [@ovaska1993b;@layne1995end], increased stomatal conductance [@layne1995end], enhanced leaf nutrient status [@turnbull2007increased] and regulatory sugar signaling [@eyles2013whole]. Similar to elevated CO~2~ experiments, these increases in *A*~n~ in defoliation experiments did not always produce increased growth due to reductions in meristem sink strength [@palacio2012fast], C limitation to mycorrhizal colonization [@markkola2004defoliation], or an overall decrease in whole plant C gain [@ovaska1993a]. These manipulations of C source activity demonstrate that changes in *A*~n~ do not always correspond with proportional responses of growth.

@@

\
Both *J*~max~ and *V*~cmax~ were significantly higher in free seedlings (30 % and 26 %, respectively) than container-grown seedlings with little variation between container volume treatments (Table `r pvetab3`). Leaf dark respiration rates were not significantly different across soil volumes (Table `r pvetab3`). The *g*~1~ parameter, generated for each seedling from the Medlyn et al [-@medlyn2011reconciling] optimal stomatal conductance model, was lowest in the free seedling treatment and was marginally different across soil volume treatments (Table `r pvetab3`).

@@

```{r table3, echo=FALSE, warning=FALSE}
dust(table3)%>%
  sprinkle_colnames("Volume (L)", 
                        "*A*~max~ ($\\mu$mol m^-2^ s^-1^)", 
                        "R ($\\mu$mol m^-2^ s^-1^)",
                        "*J*~max~",
                        "*V*~cmax~",
                        "*g*~s~ (mol m^-2^ s^-1^)",
                        "*g*~1~") %>%
  sprinkle(rows= 1, part="head",bold=TRUE)%>%
  sprinkle_print_method("markdown")
```

>>>>

\
One approach to examine the coordination of *A*~n~ and growth is to manipulate C source activity. Examples include elevated CO~2~ and partial defoliation experiments. Elevated CO~2~ has been shown to increase *A*~n~ [@drake1997more; @ainsworth2007response]; across four forest Free-Air CO~2~ Enrichment (FACE) experiments this increased photosynthetic uptake resulted in a stimulation of biomass production by 23 % on average [@norby2005forest]. Evidence from a wide range of elevated CO~2~ experiments, however, also reveals that even with an average photosynthetic enhancement of over 30 %, the biomass growth rate only increases by around 10 % [@kirschbaum2011does]. In partial defoliation experiments, increases in *A*~n~ of the remaining foliage are commonly shown, and are attributed to reduction in end-product inhibition [@iglesias2002regulation; @zhou2003changes; @handa2005test], enhanced biochemical activity [@ovaska1993b;@layne1995end;@pinkard2011gas], increased stomatal conductance [@layne1995end], enhanced leaf nutrient status [@turnbull2007increased;@pinkard2011gas] and regulatory sugar signaling [@eyles2013whole]. Similar to elevated CO~2~ experiments, these increases in *A*~n~ in defoliation experiments did not always produce increased growth due to reductions in meristem sink strength [@palacio2012fast], C limitation to mycorrhizal colonization [@markkola2004defoliation], or an overall decrease in whole plant C gain [@ovaska1993a]. These manipulations of C source activity demonstrate that changes in *A*~n~ do not always correspond with proportional responses of growth.

@@

\
Both *J*~max~ and *V*~cmax~ were significantly higher in free seedlings (30 % and 26 %, respectively) than container-grown seedlings with little variation between container volume treatments (Table `r pvetab3`). Overall, the J~max~:Vc~max~ ratio was relatively conserved across all treatments (1.6&pm;0.02), which is consistent with findings across many tree species [@medlyn1996optimal; @leuning1997scaling; @medlyn1999effects; @warren2003photosynthesis; @crous2008elevated]. Leaf dark respiration rates were not significantly different across soil volumes (Table `r pvetab3`). The *g*~1~ parameter, generated for each seedling from the Medlyn et al [-@medlyn2011reconciling] optimal stomatal conductance model, was lowest in the free seedling treatment and was marginally different across soil volume treatments (Table `r pvetab3`).

@@

```{r table3, echo=FALSE, warning=FALSE}
dust(table3)%>%
  sprinkle_colnames("Volume (L)", 
                        "*A*~max~ ($\\mu$mol m^-2^ s^-1^)", 
                        "R ($\\mu$mol m^-2^ s^-1^)",
                        "*J*~max~ ($\\mu$mol m^-2^ s^-1^)",
                        "*V*~cmax~ ($\\mu$mol m^-2^ s^-1^)",
                        "*g*~s~ (mol m^-2^ s^-1^)",
                        "*g*~1~") %>%
  sprinkle(rows= 1, part="head",bold=TRUE)%>%
  sprinkle_print_method("markdown")
```

### 2016-05-18 manuscript/thesis_pve.Rmd
thesis edits, only added to manuscript if appropriate
adds a few new cites

apparently i didnt push the CUE plots for BM yet

<!-- \ -->
<!-- Courtney E. Campany^1^, Belinda Medlyn^1^, Remko A. Duursma^1^. -->

<!-- \ -->
<!-- ^1^ Hawkesbury Institute for the Environment, University of Western Sydney, Locked Bag 1797, Penrith, NSW, Australia -->

<!-- \ -->
<!-- *Corresponding author*:  -->
<!-- Courtney Campany -->
<!-- E: courtneycampany@gmail.com -->

@@

Interpreting limitations to plant growth requires understanding the balance between carbon (C) source and sink activity. This study used manipulations of soil volume to test how growth is coupled to physiology, C allocation, and sink activity in *Eucalyptus tereticornis* seedlings. We grew individual seedlings in a large range of container sizes and planted containers flush to the soil alongside naturally planted freely-rooted (free) seedlings. We developed a seedling growth model that utilized leaf photosynthesis rates (*A~n~*) to allocate daily C uptake towards mass growth of leaves, stems and roots. Reduced soil volume was expected to induce rapid negative effects on growth and physiology compared to free seedlings. It was hypothesized that the soil volume effect would be largest in the smallest containers, negatively impacting mass partitioning belowground. An accumulation of leaf non-structural carbohydrates, resulting from reduced belowground sink strength, was expected to correlate to reductions in photosynthetic capacity. We observed a negative effect of container volume on aboveground growth soon after the experiment started. Although growth was consistently different across soil volumes, dry mass partitioning to leaves, stems and roots was unchanged after 120 days. Photosynthetic capacity was significantly reduced in containers compared to free seedlings, and was related to both reduced leaf nitrogen content and starch accumulation. We then asked whether the observed reductions in *A~n~* explained the observed differences in seedling biomass. Although belowground sink limitation resulted in a reduction of *A~n~*, the model concluded that these reductions were not large enough to explain observed growth responses. Thus, as *A~n~* and growth were not tightly coordinated, an unaccounted for pool of photosynthetic C resulted in seedlings with soil volume restriction. These results highlight the need to further utilize mass balance approaches when evaluating plant C allocation and confirm that important feedbacks exist between belowground sink strength and leaf C uptake.

<!-- ## Keywords {.unnumbered} -->
<!-- photosynthesis, growth, sink regulation, carbon allocation, soil volume -->

@@

\
In woody species, the coordination of *A~n~* and growth has been studied with manipulations of C source activity. Examples included elevated CO~2~ experiments, for example FACE [reviewed in @ainsworth2005have], and partial defoliation experiments. Elevated CO~2~ has been shown to increase *A~n~* [@drake1997more; @ainsworth2007response] and across four FACE experiments this resulted in a stimulation of 23 % in forest biomass production [@norby2005forest]. Evidence from a wide range of elevated CO~2~ experiments, however, also reveals that even with an average photosynthetic enhancement of over 30 %, the biomass growth rate only increases by around 10 % [@kirschbaum2011does]. In partial defoliation experiments, increases in *A~n~* of the remaining foliage are commonly shown, yet are attributed to various mechanisms, including reduction in end-product inhibition [@iglesias2002regulation; @zhou2003changes; @handa2005test], enhanced biochemical activity [@ovaska1993b;@layne1995end], increased stomatal conductance [@layne1995end], enhanced leaf nutrient status [@turnbull2007increased] and regulatory sugar signaling [@eyles2013whole]. However, increases in *A~n~* in defoliation experiments did not always produce increased growth due to reductions in meristem sink strength [@palacio2012fast], C limitation to mycorrhizal colonization [@markkola2004defoliation], or an overall decrease in whole plant C gain [@ovaska1993a]. These manipulations of C source activity expose unresolved issues with how changes in *A~n~* do not always correspond with proportional responses in growth.

@@

\
Six container volumes were used ranging from 5 L to 35 L, with a 22.5 cm diameter, and lengths ranging from 15 to 100 cm. Containers were constructed of PVC pipe and were filled with local top soil (described above). Soil in each container was packed to achieve a target soil bulk density that matched local soil conditions of 1.7 g cm^-3^. A Imidacloprid (BAYER CropScience) insecticide tablet was planted 5 cm below the roots of each seedling. Containers were planted flush with the soil surface inside metal sleeves, designed to minimize excess air space between the container and outside soil while also allowing for container removal. This allowed for soil temperatures in containers to reflect conditions of naturally planted (free) seedlings. Each experimental block (n=7) contained a complete replicate set of six container volumes as well as one free seedling, with 1 m^2^ spacing. For each free seedling, used as the control, a 1 m^2^ subplot was excavated to the hard layer and replaced with the same soil used in each container. A border of root exclusion material was buried 0.25 m deep and extended 0.25 m above the ground surface around each subplot to exclude local vegetation, which was further kept out by periodic weeding.

@@

\
Leaf dark respiration rates (*R*) was measured on each seedling during the same dates as AC~i~ curves. Freshly detached leaves were collected at least 1 hour after sundown and placed inside a conifer chamber attached to the Licor 6400. Measurements were taken at a reference [CO~2~] of 400 $\mu$l l^-1^ while leaf temperature was maintained at current ambient conditions. Reported values of *R* are standardized rates at 25 &deg;C using a Q~10~ value (1.86) developed for these seedlings in a separate experiment (Drake et al. unpublished). Leaf area and dry mass were recorded for each leaf during gas exchange campaigns.

@@

\
(2)
$$R = \Sigma(R_c~M_c)$$
where *R~c~* is published or local tissue respiration rates of fine roots, coarse roots or stems (Table `r pvetabS`, g C g mass^-1^ d^-1^) and M~c~ is the standing biomass of each component (g). Leaf respiration is represented in the calculation of C~day~. The change in individual component biomass (M~c~), here solved on a daily time step, is given by

@@

\
C~day~ was predicted by using a coupled photosynthesis - stomatal conductance model [@farquhar1980biochemical;@medlyn2011reconciling] with the 'plantecophys' package [@duursma2015] in R with the mean photosynthetic parameters (J~max~, Vc~max~, *R* and g~1~) for each treatment and meteorological data from an onsite weather station. J~max~ and Vc~max~ were estimated from AC~i~ curves (explained above), *R* was empirically measured and the g~1~ parameter was generated by fitting the optimal stomatal conductance model from [@medlyn2011reconciling] with observed g~s~ values. Methods of the coupled leaf gas exchange model are also described in Duursma et al [-@duursma2014peaked]. Combined with the meteorological parameters; PPFD, air temperature, and relative humidity, at 15 min intervals, leaf *A~n~* rates ($\mu$mol CO~2~ m^-2^ s^-1^) were then predicted for each soil volume treatment. C~day~ was calculated by converting predicted rates to mass C gain over 15 min time steps (g m^-2^) and then summed for 24 h. This resulted in 120 unique values of C~day~ for each soil volume treatment, one value for each day of the experiment. Thus, each daily time step for model runs included a value of C~day~ that represented both treatment specific photosynthetic parameters and meteorological constraints across the duration of the experiment.

\
It was further necessary to calculate a self-shading parameter ($\sigma$~s~) when scaling leaf *A~n~* with total plant leaf area. This was accomplished by utilizing 61 previously digitized *Eucalyptus* seedlings, covering 5 total species which include *E. tereticornis*, from Duursma et al. [-@duursma2012light] to run in 'YplantQMC' package [@YplantQMC] in R to build a 3D plant structure based on digitized metrics of plant allometry and crown structure. Using the same treatment specific physiological parameters listed above, 'YplantQMC' outputs total *A~n~*, using total leaf area, for seedlings assuming self-shading as well as for a full sun large horizontal leaf. The ratio of total *A~n~* with self-shading to horizontal leaf was then used to calculate $\sigma$~s~ for each of the 61 digitized seedlings, independently for each of the seven soil volume treatments. Next, the linear relationship between $\sigma$~s~ and total leaf area was determined across digitized seedlings, within each treatment. For the growth model, $\sigma$~s~ was then predicted for each daily time step using the previous days cumulative leaf area and this value  was then applied to C~day,i~. All default parameters used in model simulations are reported in Table `r pvetabS`.

@@

```{r table3, echo=FALSE, warning=FALSE}
dust(table3)%>%
  sprinkle_colnames("Volume (L)", 
                        "A~max~ ($\\mu$mol m^-2^ s^-1^)", 
                        "*R* ($\\mu$mol m^-2^ s^-1^)",
                        "J~max~",
                        "Vc~max~",
                        "g~s~ (mol m^-2^ s^-1^)",
                        "g~1~") %>%
  sprinkle(rows= 1, part="head",bold=TRUE)%>%
  sprinkle_print_method("markdown")
```

@@

\
Both J~max~ and Vc~max~ were significantly higher in free seedlings (30 % and 26 %, respectively) than container-grown seedlings with little variation between container volume treatments (Table `r pvetab3`). Leaf dark respiration rates were not significantly different across soil volumes (Table `r pvetab3`). The g~1~ parameter, generated for each seedling from the Medlyn et al [-@medlyn2011reconciling] optimal stomatal conductance model, was lowest in the free seedling treatment and was marginally different across soil volume treatments (Table `r pvetab3`).

@@

```{r model_scenarios, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
source("master_scripts/massmodel_optimize_scenarios.R")
```  
\
\
\
**Figure 2.S1**. Sensitivity testing of the seedling growth model to different carbon allocation strategies including; constraints of leaf mass fraction to treatment specific final harvest values (a) and increases in respiration of non-leaf tissue components by 50 % (b).  Open and filled symbols represent default model and harvest values, while shaded symbols represent model sensitivity to each scenario by soil volume treatment. Both seedling carbon mass and daily carbon assimilation were first scaled to the free seedling control.

>>>>

@@

Interpreting limitations to plant growth requires understanding the balance between carbon (C) source and sink activity. This study used manipulations of soil volume to test how growth is coupled to physiology, C allocation, and sink activity in *Eucalyptus tereticornis* seedlings. We grew individual seedlings in a large range of container sizes and planted containers flush to the soil alongside naturally planted freely-rooted (free) seedlings. We developed a seedling growth model that utilized leaf photosynthesis rates (*A~n~*) to allocate daily C uptake towards mass growth of leaves, stems and roots. Reduced soil volume was expected to induce rapid negative effects on growth and physiology compared to free seedlings. It was hypothesized that the soil volume effect would be largest in the smallest containers, negatively impacting mass partitioning belowground. An accumulation of leaf non-structural carbohydrates, resulting from reduced belowground sink strength, was expected to correlate to reductions in photosynthetic capacity. We observed a negative effect of container volume on aboveground growth soon after the experiment started. Although growth was consistently different across soil volumes, dry mass partitioning to leaves, stems and roots was unchanged after 120 days. Photosynthetic capacity was significantly reduced in containers compared to free seedlings, and was related to both reduced leaf nitrogen content and starch accumulation. We then asked whether the observed reductions in *A~n~* explained the observed differences in seedling biomass. Although belowground sink limitation resulted in a reduction of *A~n~*, the model concluded that these reductions were not large enough to explain observed growth responses. As *A~n~* and growth were not tightly coupled, an unaccounted for pool of photosynthetic C resulted was predicted in seedlings with soil volume restriction. These results highlight the need to further utilize mass balance approaches when evaluating plant C allocation and confirm that important feedbacks exist between belowground sink strength and leaf C uptake.

@@

\
In woody species, the coordination of *A~n~* and growth has been studied with manipulations of C source activity. Examples included elevated CO~2~ experiments, for example FACE [reviewed in @ainsworth2005have], and partial defoliation experiments. Elevated CO~2~ has been shown to increase *A~n~* [@drake1997more; @ainsworth2007response] and across four FACE experiments this resulted in a stimulation of 23 % in forest biomass production [@norby2005forest]. Evidence from a wide range of elevated CO~2~ experiments, however, also reveals that even with an average photosynthetic enhancement of over 30 %, the biomass growth rate only increases by around 10 % [@kirschbaum2011does]. In partial defoliation experiments, increases in *A~n~* of the remaining foliage are commonly shown, yet are attributed to various mechanisms, including reduction in end-product inhibition [@iglesias2002regulation; @zhou2003changes; @handa2005test], enhanced biochemical activity [@ovaska1993b;@layne1995end; @pinkard2011gas], increased stomatal conductance [@layne1995end], enhanced leaf nutrient status [@turnbull2007increased; @pinkard2011gas] and regulatory sugar signaling [@eyles2013whole]. However, increases in *A~n~* in defoliation experiments did not always produce increased growth due to reductions in meristem sink strength [@palacio2012fast], C limitation to mycorrhizal colonization [@markkola2004defoliation], or an overall decrease in whole plant C gain [@ovaska1993a]. These manipulations of C source activity expose unresolved issues with how changes in *A~n~* do not always correspond with proportional responses in growth.

@@

\
Six container volumes were used ranging from 5 L to 35 L, with a 22.5 cm diameter, and lengths ranging from 15 to 100 cm. Containers were constructed of PVC pipe and were filled with local top soil (described above). Soil in each container was packed to achieve a target soil bulk density that matched local soil conditions of 1.7 g cm^-3^. A Imidacloprid (BAYER CropScience) insecticide tablet was planted 5 cm below the roots of each seedling. Containers were planted flush with the soil surface inside metal sleeves, designed to minimize excess air space between the container and outside soil while also allowing for container removal. This allowed for soil temperatures in containers to reflect conditions of naturally planted (free) seedlings. Each experimental block (n=7) contained a complete replicate set of six container volumes as well as one free seedling, with 1 m^2^ spacing. For each free seedling, used as the control, a 1 m^2^ subplot was excavated to the hard layer and replaced with the same soil used in each container. This ensured that any possible feedbacks from soil disturbance would be similar between seedlings in containers and free seedlings. A border of root exclusion material was buried 0.25 m deep and extended 0.25 m above the ground surface around each subplot to exclude local vegetation, which was further kept out by periodic weeding.

@@

\
Leaf dark respiration rates (*R*) was measured on each seedling during the same dates as AC~i~ curves. Freshly detached leaves were collected at least 1 hour after sundown and placed inside a conifer chamber attached to the Licor 6400. This method increases the measureable surface area of each leaf, beyond the standard leaf chamber, to accurately quantify *R*. Measurements were taken at a reference [CO~2~] of 400 $\mu$l l^-1^ while leaf temperature was maintained at current ambient conditions. Reported values of *R* are standardized rates at 25 &deg;C using a Q~10~ value (1.86) developed for these seedlings in a separate experiment (Drake et al. unpublished). Leaf area and dry mass were recorded for each leaf during gas exchange campaigns.

@@

\
(2)
$$R = \Sigma(R_c~M_c)$$
where *R~c~* is tissue respiration rates of fine roots, coarse roots or stems (Table `r pvetabS`, g C g mass^-1^ d^-1^) and M~c~ is the standing biomass of each component (g). Tissue respiration rates were not directly measured in this experiment, so published or local default values from Eucalyptus species were used. Leaf respiration is represented in the calculation of C~day~. The change in individual component biomass (M~c~), here solved on a daily time step, is given by

@@

\
C~day~ was predicted by using a coupled photosynthesis - stomatal conductance model [@farquhar1980biochemical;@medlyn2011reconciling] with the 'plantecophys' package [@duursma2015] in R with the mean photosynthetic parameters (J~max~, Vc~max~, *R* and g~1~) for each treatment and meteorological data from an onsite weather station. J~max~ and Vc~max~ were estimated from AC~i~ curves (explained above), *R* was empirically measured and the g~1~ parameter, describing the plants water-use strategy, was generated by fitting the optimal stomatal conductance model from [@medlyn2011reconciling] with observed g~s~ values. Methods of the coupled leaf gas exchange model are also described in Duursma et al [-@duursma2014peaked]. Combined with the meteorological parameters; PPFD, air temperature, and relative humidity, at 15 min intervals, leaf *A~n~* rates ($\mu$mol CO~2~ m^-2^ s^-1^) were then predicted for each soil volume treatment. C~day~ was calculated by converting predicted rates to mass C gain over 15 min time steps (g m^-2^) and then summed for 24 h. This resulted in 120 unique values of C~day~ for each soil volume treatment, one value for each day of the experiment. Thus, each daily time step for model runs included a value of C~day~ that represented both treatment specific photosynthetic parameters and meteorological constraints across the duration of the experiment.

\
It was further necessary to calculate a self-shading parameter ($\sigma$~s~) when scaling leaf *A~n~* with total plant leaf area. Accurately modelling canopy photosynthesis requires inclusion of the heterogeneous nature of light availability that occurs from self-shading and the limitations this then imposes on leaf *A~n~* [@de1997simple; @marchiori2014photosynthetic]. This was accomplished by utilizing 61 previously digitized *Eucalyptus* seedlings, covering 5 total species which include *E. tereticornis*, from Duursma et al. [-@duursma2012light] to run in 'YplantQMC' package [@YplantQMC] in R to build a 3D plant structure based on digitized metrics of plant allometry and crown structure. Using the same treatment specific physiological parameters listed above, 'YplantQMC' outputs total *A~n~*, using total leaf area, for seedlings assuming self-shading as well as for a full sun large horizontal leaf. The ratio of total *A~n~* with self-shading to horizontal leaf was then used to calculate $\sigma$~s~ for each of the 61 digitized seedlings, independently for each of the seven soil volume treatments. Next, the linear relationship between $\sigma$~s~ and total leaf area was determined across digitized seedlings, within each treatment. For the growth model, $\sigma$~s~ was then predicted for each daily time step using the previous days cumulative leaf area and this value  was then applied to C~day,i~. All default parameters used in model simulations are reported in Table `r pvetabS`.

@@

```{r table3, echo=FALSE, warning=FALSE}
dust(table3)%>%
  sprinkle_colnames("Volume (L)", 
                        "A~max~ ($\\mu$mol m^-2^ s^-1^)", 
                        "*R* ($\\mu$mol m^-2^ s^-1^)",
                        "J~max~ ($\\mu$mol m^-2^ s^-1^)",
                        "Vc~max~ ($\\mu$mol m^-2^ s^-1^)",
                        "g~s~ (mol m^-2^ s^-1^)",
                        "g~1~") %>%
  sprinkle(rows= 1, part="head",bold=TRUE)%>%
  sprinkle_print_method("markdown")
```

@@

\
Both J~max~ and Vc~max~ were significantly higher in free seedlings (30 % and 26 %, respectively) than container-grown seedlings with little variation between container volume treatments (Table `r pvetab3`). Overall, the J~max~:Vc~max~ ratio was relatively conserved across all treatments (1.6&pm;0.02), which is consistent with findings across many tree species [@medlyn1996optimal; @leuning1997scaling; @medlyn1999effects; @warren2003photosynthesis; @crous2008elevated]. Leaf dark respiration rates were not significantly different across soil volumes (Table `r pvetab3`). The g~1~ parameter, generated for each seedling from the Medlyn et al [-@medlyn2011reconciling] optimal stomatal conductance model, was lowest in the free seedling treatment and was marginally different across soil volume treatments (Table `r pvetab3`).

@@

```{r model_scenarios, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
source("clean Scripts/massmodel_optimize_scenarios.R")
```  
\
\
\
**Figure 2.S1**. Sensitivity testing of the seedling growth model to different carbon allocation strategies including; constraints of leaf mass fraction to treatment specific final harvest values (a) and increases in respiration of non-leaf tissue components by 50 % (b).  Open and filled symbols represent default model and harvest values, while shaded symbols represent model sensitivity to each scenario by soil volume treatment. Both seedling carbon mass and daily carbon assimilation were first scaled to the free seedling control.
